The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
fill acknowledge

We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J.
Hogg, and L. Newediuk for their comments on previous versions of this manuscript
as well as D. C. Schneider for inspiration and helpful discussions about scale.
Funding for this study was provided by a Vanier Canada Graduate Scholarship to
QMRW and a NSERC Discovery Grant to EVW.

>>>>

We respectfully acknowledge the territory in which data were collected and
analyzed as the ancestral homelands of the Beothuk and the Island of
Newfoundland as the ancestral homelands of the Mi’kmaq and Beothuk. We thank
members of the Newfoundland and Labrador Wildlife Division, including S. Moores,
B. Adams, W. Barney, and J. Neville for facilitating animal captures and for
logistical support in the field. We also thank all members of the Wildlife
Evolutionary Ecology Lab, including J. Hendrix, K. Kingdon, S. Boyle, J.
Balluffi-Fry, C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for their
comments on previous versions of this manuscript as well as D. C. Schneider for
inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.
